\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual All-Loop Integrands

### 2023-09-21 notes/2loopNLSM.tex
Merged the two ZM footnotes in the pion section.

\ace{Lets tighten up this paragraph a bit, especially the second half}
It is tempting to try to match the pion four-point two-loop integrand to ZM
on the cuts, but given that the cuts only probe the on-shell four-point
amplitude, which is either subtle or vanishes for ZM, it is better to
compare the off-shell numerators directly.  As local functions, the
numerators never suffer from any of the subtleties of on-shell 2D
kinematics.  Since the physical cuts are difficult to compare, ZM
theory is being used here simply as a tool to eliminate generalized
gauge freedom; ZM theory has the right power counting and kinematic
structure in 2D to compare against.  Since ZM theory is only being
used for the kinematical structure of its numerators, it is natural to
introduce a proportionality constant $z$ between the NLSM and ZM
numerators $n_\text{NLSM} \vert_{2D} = z ~ n_\text{ZM}$.  The
parameter $z$, which would normally be fixed on cuts, effectively
encodes the discrepancy between the coupling constants of the two
theories.\footnote{Floating the proportionality parameter $z$ is also
  motivated because ZM is believed to be quantum mechanically
  different from NLSM even though they are dual classically in two
  dimensions \cite{Nappi:1979ig}.}  This introduces an extra degree of
freedom into the problem.  Mechanically, the pion numerator is matched
to ZM by first taking every possible assignment of right and left
movers for the external particles and then restricting the pion
numerator to 2D.  The loop momenta are restricted to 2D but left
off-shell.  After performing the 2D matching, there are only 365
parameters of generalized gauge freedom.

The loop momentum structure of ZM theory provides one final hint for
simplifying the pion numerators.  A generic term in the ZM numerator
(of either basis graph) looks schematically like
\begin{equation}
\label{eq:ZMLoopPowCount}
\ell_1^m \ell_2^n k^{12-(m+n)} \text{ where } 5 \leq m+n \leq 8,
\end{equation}
whereas a generic set of local, cubic Feynman rules could have
produced terms with up to $m+n=12$ powers of loop momenta.  When the
pion numerator is forced to have the loop power counting structure in
\cref{eq:ZMLoopPowCount} of ZM theory, the number of generalized gauge
freedom parameters reduces to 58.  The pion numerator appearing in the
ancillary files makes exactly this choice.\footnote{When the four-point
  pion amplitude is normalized to $-k_1\cdot k_2$ and the ZM vertex is
  normalized to $k_1^\mu \varepsilon_{\mu\nu}k_2^\nu$, the parameter
  $z$ is fixed to $216/565$, which is clearly unrelated to the
  difference in coupling constants.} \ace{Is this actually where we
  want this particular footnote to appear?}

>>>>

\ace{Lets tighten up this paragraph a bit, especially the second half}
It is tempting to try to match the pion four-point two-loop integrand
to ZM on the cuts, but given that the cuts only probe the on-shell
four-point amplitude, which is either subtle or vanishes for ZM, it is
better to compare the off-shell numerators directly.  As local
functions, the numerators never suffer from any of the subtleties of
on-shell 2D kinematics.  Since the physical cuts are difficult to
compare, ZM theory is being used here simply as a tool to eliminate
generalized gauge freedom; ZM theory has the right power counting and
kinematic structure in 2D to compare against.  Since ZM theory is only
being used for the kinematical structure of its numerators, it is
natural to introduce a proportionality constant $z$ between the NLSM
and ZM numerators $n_\text{NLSM} \vert_{2D} = z ~ n_\text{ZM}$.  The
parameter $z$, which would normally be fixed on cuts, effectively
encodes the discrepancy between the coupling constants of the two
theories.\footnote{Floating the proportionality parameter $z$ is also
  motivated because ZM is believed to be quantum mechanically
  different from NLSM even though they are dual classically in two
  dimensions \cite{Nappi:1979ig}.  When the four-point
  pion amplitude is normalized to $-k_1\cdot k_2$ and the ZM vertex is
  normalized to $k_1^\mu \varepsilon_{\mu\nu}k_2^\nu$, the parameter
  $z$ is fixed to $216/565$, which is clearly unrelated to the
  difference in coupling constants.}  This introduces an extra degree of
freedom into the problem.  Mechanically, the pion numerator is matched
to ZM by first taking every possible assignment of right and left
movers for the external particles and then restricting the pion
numerator to 2D.  The loop momenta are restricted to 2D but left
off-shell.  After performing the 2D matching, there are only 365
parameters of generalized gauge freedom.

The loop momentum structure of ZM theory provides one final hint for
simplifying the pion numerators.  A generic term in the ZM numerator
(of either basis graph) looks schematically like
\begin{equation}
\label{eq:ZMLoopPowCount}
\ell_1^m \ell_2^n k^{12-(m+n)} \text{ where } 5 \leq m+n \leq 8,
\end{equation}
whereas a generic set of local, cubic Feynman rules could have
produced terms with up to $m+n=12$ powers of loop momenta.  When the
pion numerator is forced to have the loop power counting structure in
\cref{eq:ZMLoopPowCount} of ZM theory, the number of generalized gauge
freedom parameters reduces to 58.  The pion numerator appearing in the
ancillary files makes exactly this choice. \ace{Is this actually where we
  want this particular footnote to appear?}
